|

### 2020-12-09 03-Chp-Systematic-Review-Tools.Rmd
Updates end-of-day

In addition the

Developing new tools for facilitating evidence synthesis will benefit patients by speeding up the speed with which systematic reviews are produced. A recent study put the mean duration of a systematic review project, from date of registration to date of publication is 67.3 weeks.[@borah2017] A large proportion of this time will be spent on manual tasks such as running searches and extracting records, title and abstract screening, and data extraction - therefore, efforts to increase the efficiency of the process should focus on process that can be automated.

@@

One of the key features of the `medrxivr` is the ability for users to export the results of their

@@

By implementing the tool described above as both as an R package and a `Shiny` web app, the functionality is available to evidence synthesists with varying levels of ability in R. These tools serve as an example of the advantages of “packaging” the R scripts that evidence synthesists often create for personal use.[@wickham2015r] In the case of `medrxivr`, it is likely that several other evidence synthesists had written scripts that have a similar functionality - in fact, in the course of its development, one other researcher that has done so was identified. This duplication of time and effort is inefficient, and creating and sharing well-documented R packages represents one way to reduce this inefficiency. Taking this approach one step further, `Shiny` apps represent a straightforward way to provide a user-friendly GUI for a newly created R package within a very short time-frame, expanding the potential pool of users of the package to anyone with an internet connection.

@@

>>>>

More generally, developing new tools for facilitating evidence synthesis will benefit patients by speeding up the speed with which systematic reviews are produced. A recent study put the mean duration of a systematic review project, from date of registration to date of publication is 67.3 weeks.[@borah2017] A large proportion of this time will be spent on manual tasks such as running searches and extracting records, title and abstract screening, and data extraction - therefore, efforts to increase the efficiency of the process should focus on process that can be automated.

@@

One of the key features of the `medrxivr` is the ability for users to easily export the results of their systematic search to a reference manager. While it is a seemingly simple request, this is is one of the key ways in which `medrxivr` - as it was built with systematic reviews specifically in mind, it is

@@

By implementing the tool described above as both as an R package and a `Shiny` web app, the functionality is available to evidence synthesists with varying levels of ability in R. These tools serve as an example of the advantages of “packaging” the R scripts that evidence synthesists often create for personal use.[@wickham2015r] In the case of `medrxivr`, it is likely that several other evidence synthesists had written scripts that have a similar functionality - in fact, in the course of its development, one other researcher that has done so was identified (xxxx xxxx, author of the `rbiorxiv` pacakge).[@rbiorxiv]

``` {r, eval = TRUE, echo = FALSE}

t<-rbiorxiv::biorxiv_summary()

```

This duplication of time and effort is inefficient, and creating and sharing well-documented R packages represents one way to reduce this inefficiency. Taking this approach one step further, `Shiny` apps represent a straightforward way to provide a user-friendly GUI for a newly created R package within a very short time-frame, expanding the potential pool of users of the package to anyone with an internet connection.

@@

test

### 2020-12-09 04-Chp2-Systematic-Review.Rmd
Updates end-of-day

>>>>

Consideration of the potential impact of the magnitude and direct of unaddressed confounders/bias is not a major stretch from what is already happening in the assessment of the quality of evidence (GRADE) framework. Wihtin GRADE the overall quality of evidence can be upgraded when there is deemed to be **will need to confirm this.l** [@guyatt2011]
